### 2018-05-06 papers/synth/conclusion.tex

In this paper, we presented encodings of the synthesis problems
that may rise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs. 
%
We will take this tool to the biologists and develop wet experiments 
that may validate some synthesis results from the tool.
%
Our model of VTSs are static graphs.
%
In future, we will study the dynamic behaviours of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.

>>>>

In this paper, we presented encodings of the synthesis problems
that may rise from VTSs.
%
We demonstrated that our tool based on the encodings
scale up to the relevant sizes of the VTSs for some synthesis queries.
%
Our tool timedout on larger examples.
%
We are working to improve the performance of our tool.
%
We will take this tool to the biologists and develop wet experiments 
that may validate some synthesis results from the tool.
%
Our model of VTSs are static graphs.
%
In future, we will study the dynamic behaviours of VTSs.
%
It will allow us to predict behaviors after the perturbations in the VTSs
and more ways to test the predicted synthesis results.
